---
title: "cross_validation"
author: "TritonD"
date: "11/12/2019"
output: html_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)
set.seed(1)
```

generate a dataset
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```

# training and testing
```{r}
train_df = sample_frac(nonlin_df, size=0.8)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

# fit three models of varying goodness
```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```
y is a smooth function of x


look at some fits
```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

# cross-validation
```{r}
rmse(linear_mod, test_df)
```
root mean squared error, larger number is worse

```{r}
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```
always pick the model that fit the testing dataset better
put more variables always make rmse go down in training dataset

# do this all using modelr
```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
```


one note about resample
```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble
```
[[1]] indicates this is the first training set


```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
cv_df
```

try fitting linear model of all of these
take training model, apply linear model every single time
```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(y ~ x, data = .x)),
         smooth_mod  = map(train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y)))
```

# child growth
```{r}
child_growth = read_csv("./nepalese_children.csv")
```

```{r}
child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```


